%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}


\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Eitan Seri-Levi} \\ \vspace{1pt}
    \small 310-619-9141 $|$ \href{mailto:eserilev@gmail.com}{\underline{eserilev@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/eitan-seri-levi/}{\underline{linkedin.com/in/eitan-seri-levi}} $|$
    \href{https://github.com/eserilev}{\underline{github.com/eserilev}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Santa Cruz}{Santa Cruz, CA}
      {Bachelor of Science in Computer Science, Minor in Physics}{Sep. 2010 -- June 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{Jan 2024 -- Present}
      {Sigma Prime}{}
      \resumeItemListStart 
        \resumeItem{Contributed to Lighthouse, an Ethereum consensus client implementation written in Rust.}
        \resumeItem{Contributed to rust-libp2p, a peer to peer networking implementation written in Rust.}
    \resumeItemListEnd

    \resumeSubheading
      {Director of Product Engineering}{Dec 2021 -- May 2024}
      {Dcentralab}{}
      \resumeItemListStart
        \resumeItem{Designed and built the worlds first BSC to Cardano bridge. Currently the Cardano bridge can be used to bridge tokens to/from 15 different EVM networks and has facilated hundreds of millions of dollars in transaction volume.}
        \resumeItem{Designed and built Chainport stablecoin bridge functionality. The contracts storing cross-chain stablecoin liquidity utilize a stableswap algorithim to minimize slippage.}
        \resumeItem{Built a mechanism that checks cross chain token reserves and issues automatic contract freezes if token balances are incorrect.}
        \resumeItem{Built Chainports cross-chain fee infrastructure which allows users to pay for bridge fees using Chainports native token, PORTX.}
        \resumeItem{Managed a team of several frontend, backend and solidity engineers. Provided mentorship, participated in code reviews and created/reviewed technical specifications.}
        \resumeItem{After December 2023, my role moved from full time to part time consultant.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
    
    \resumeSubheading
      {Software Engineer}{Sep 2018 -- Dec 2023}
      {Winc Wines}{}
      \resumeItemListStart
        \resumeItem{Helped design and build Wincs monthly subscription based business model.}
        \resumeItem{Helped design and build Wincs custom wine recommendation engine.}
        \resumeItem{Developed consumer facing software using Angular, Node.js, .NET and Azure.}
        \resumeItem{After December 2021, my role moved from full time to part time.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Open Source Contributions}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Lighthouse} $|$ \emph{Rust}}{}
          \resumeItemListStart
            \resumeItem{Implemented the Beacon API block v3 endpoint. This endpoint is part of the upcoming Ethereum Deneb upgrade.}
            \resumeItem{Added SSZ support to the full block production flow. Based on benchmarks related to encoding/decoding of signed blinded beacon block payloads with SSZ vs JSON, SSZ has been shown to be roughly 40x faster.}
            \resumeItem{Added several new database implementation to the Slasher backend. The new database implementations include Redb and Sqlite.}
            \resumeItem{Modularized the Beacon Node backend to allow for new database implementations to be added in the future.}
            \resumeItem{Implemented several Beacon API endpoints related to validator rewards, lightclients and more.}
            \resumeItem{Made over 15 separate contributions to the Lighthouse codebase.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{rust-libp2p} $|$ \emph{Rust}}{}
          \resumeItemListStart
            \resumeItem{Added tracing/structured logging to the rust-libp2p library which provides developers with much more informative/helpful logs.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Rust, Python, Solidity, C\#, Typescript, SQL} \\
     \textbf{Developer Tools}{: Git, Docker, AWS, Azure, Vim, VS Code} \\
     \textbf{Libraries/Frameworks}{: web3, hardhat, reqwest, warp, rusqlite, redb, lmdb, mongo, pycardano, AWS lambda}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}